Utilizing Convolution for Obstacle Avoidance during Robotic Manipulator Movement

### 2023-07-20 Articles/ERK/erk.tex
.

\usepackage{easyReview} % for \comment, \alert, etc.

@@

\begin{abstract}{Abstract}
For the papers written in Slovene language an English title and abstract is required. The abstract should be no more than 200 words.

We accept only electronic submissions in pdf (without password protection) or Microsoft Word format. Submission form can be found on ERK web page \cite{ERK}.
\end{abstract}

@@

APF for EE task.

>>>>

@@

\begin{abstract}{Abstract}
\todocomment{ADD}
\end{abstract}

@@
